Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Moved estimates based on supercop results to Results chapter

\section{\ac{SUPERCOP} benchmarks}

@@

@@

\section{\ac{SUPERCOP} results}

We see in Tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-LAFS uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume a worst case scenario of hashing 32 bytes, where the cycles/byte
count is exactly the same as for 8 bit median we get:

$$\frac{median * size + 179.62*32}{size} = SHA256d estimate$$

Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. What we can see that for lower lengths of data,
more of the candidates are faster than double \ac{SHA}-256. However, given the
practical situation that Tahoe-\ac{LAFS} is a file system, most files processed
will be larger than the file sizes estimated here. Not all hashing
operations in Tahoe-\ac{LAFS} are strictly dependant on the original file size,
which would mean that all candidates would have a chance of outperforming
double \ac{SHA}-256. However this estimate is worst case, which leads us to
believe that at least for larger input sizes (over 1536) only the five fastest
candidates will have a change of outperforming double \ac{SHA}-256.

>>>>

\section{SUPERCOP benchmarks}

@@

\subsection{Estimates}

We see in Tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8} that in general BLAKE, \ac{BMW}, Luffa, Shabal and Simd
outperform \ac{SHA}-256. However, given that Tahoe-\ac{LAFS} uses double
\ac{SHA}-256, this means that it will also have to hash another 32 bytes for
every message it hashes. Since \ac{SUPERCOP} does not have a benchmark for 32
byte messages, we will have to estimate the amount of cycles required for this.
If we assume a worst case scenario of hashing 32 bytes, where the cycles per
byte count is exactly the same as for 8 bit median, we get:

$$\frac{median * size + 179.62*32}{size} = SHA256d\ estimate$$

Estimates based on this calculation are shown in Table
\ref{tbl:supercop:sha256d}. For shorter lengths of data,
more of the candidates are faster than double \ac{SHA}-256. Nevertheless, given
the practical situation that Tahoe-\ac{LAFS} is a file system, most files
processed will be larger than the file sizes estimated here. Not all hashing
operations in Tahoe-\ac{LAFS} are strictly dependant on the original file size,
which would mean that all candidates would have a chance of outperforming double
\ac{SHA}-256. This estimate is however worst case, which leads us to believe
that at least for larger input sizes (i.e. over 1536 bytes) only the five
fastest candidates will have a chance of outperforming double \ac{SHA}-256.

@@

% TODO: Intro
